### 2025-12-15 tex/manuscript-final.tex
Prepare final manuscript

\stop % This is the originally submitted manuscript which should not be re-compiled.

@@

\begin{center}
	\begin{minipage}{0.88\linewidth}
		\begin{center}
			\LARGE
			The Malaysian Election Corpus (\acronymend):\\Federal and State-Level Election Results\\from 1955 to 2025 \\[0.21in]
			\Large
			Thevesh Thevananthan\footnotemark$^{\text{\Letter}}$\\[0.15in]
		\end{center}
		\large
		Empirical research and public knowledge on Malaysia's elections have long been constrained by a lack of high-quality open data, particularly in the absence of a Freedom of Information framework. This paper introduces the Malaysian Election Corpus (MECo), an open-access panel database covering all federal and state general elections since 1955, as well as by-elections since 2008. MECo includes candidate- and constituency-level data for 9,704 electoral contests across seven decades, standardised with unique identifiers for candidates, parties, and coalitions. The database also provides summary statistics for each contest (electorate size, voter turnout, majority size, rejected ballots, unreturned ballots), key demographic data for candidates (age, gender, ethnicity), and lineage data for political parties. MECo is the most well-curated open database on Malaysian elections to date, and will unlock new opportunities for research, data journalism, and civic engagement.
	\end{minipage}
\end{center}

@@

In this paper, I address this gap by providing the Malaysian Election Corpus (MECo),\cite{meco_dataset} the first comprehensive open database of Malaysian election results at the federal and state level. MECo is intended as a living resource which provides the go-to empirical foundation for research and journalism on Malaysian elections. The database covers \textit{all} general elections since the pre-independence general election in 1955, and all \TOTALCONTESTSBYELEC\space by-elections since the 12th federal general election in 2008. In total, it records \UNIQUECANDIDATES\space unique candidates representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to 2025.

@@

This validation procedure also revealed \TOTALCORRECTIONS\space contests (excluding elections before 1960 which did not report $I$, and the 2006 Sarawak state general election, which did not report $I$, $U$, or $R$) for which the data was digitised accurately based on my source material, but which nevertheless failed to satisfy Equation (\ref{eq:validation}). These errors presumably occurred due to mistakes in data entry which were not caught and corrected during the original publication process. In order to ensure a clean dataset, I applied a standard correction -- for all \TOTALCORRECTIONS\space contests failing validation, I adjusted the number of ballots issued (as documented in \texttt{corrections.csv}) such that Equation (\ref{eq:validation}) holds. I chose \texttt{ballots\_issued} as the variable to adjust for two reasons. First, until the 1989 amendment of the Elections (Conduct of Elections) Regulations 1981 (implemented at the 1989 federal general election), the number of unreturned ballots was not reported (and thus assumed to be 0). Second, because the number of rejected ballots is very small relative to the number of ballots issued, using rejected ballots as the adjusted variable would have resulted in a much larger correction in percentage terms -- specifically, the correction would have required a 20\% change to the number of rejected ballots on average (with several exceeding 50\%), relative to a 0.6\% change to the number of ballots issued (with only one above 5\%, and none above 20\%).

>>>>

@@

\begin{center}
	\begin{minipage}{0.88\linewidth}
		\begin{center}
			\LARGE
			The Malaysian Election Corpus (\acronymend):\\Federal and State-Level Election Results\\from 1955 to the Present \\[0.21in]
			\Large
			Thevesh Thevananthan\footnotemark$^{\text{\Letter}}$\\[0.15in]
		\end{center}
		\large
		Empirical research and public knowledge on Malaysia's elections have long been constrained by a lack of high-quality open data, particularly in the absence of a Freedom of Information framework. This paper introduces the Malaysian Election Corpus (MECo), an open-access panel database covering all federal and state general elections since 1955, as well as by-elections since 2008. MECo includes candidate- and constituency-level data for 9,704 electoral contests across seven decades, standardised with unique identifiers for candidates, parties, and coalitions. The database also provides summary statistics for each contest (electorate size, voter turnout, majority size, rejected ballots, unreturned ballots), key demographic data for candidates (age, gender, ethnicity), and lineage data for political parties. MECo is the most well-curated open database on Malaysian elections to date, and will unlock new opportunities for research, data journalism, and civic engagement.
	\end{minipage}
\end{center}

@@

In this paper, I address this gap by providing the Malaysian Election Corpus (MECo),\cite{meco_dataset} the first complete open database of Malaysian election results at the federal and state level. MECo is intended as a living resource which provides the go-to empirical foundation for research and journalism on Malaysian elections. The database covers \textit{all} general elections and by-elections since the pre-independence general election in 1955. In total, it records \UNIQUECANDIDATES\space unique candidates representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to the present.

@@

This validation procedure also revealed \TOTALCORRECTIONS\space contests (excluding elections before 1960 which did not report $I$, and the 2006 Sarawak state general election, which did not report $I$, $U$, or $R$) for which the data was digitised accurately based on my source material, but which nevertheless failed to satisfy Equation (\ref{eq:validation}). These errors presumably occurred due to mistakes in data entry which were not caught and corrected during the original publication process. In order to ensure a clean dataset, I applied a standard correction -- for all \TOTALCORRECTIONS\space contests failing validation, I adjusted the number of ballots issued (as documented in \texttt{corrections.csv}) such that Equation (\ref{eq:validation}) holds. I chose \texttt{ballots\_issued} as the variable to adjust for two reasons. First, until the 1981 amendment of the Elections (Conduct of Elections) Regulations (implemented from the 1990 federal general election onwards), the number of unreturned ballots was not reported (and thus assumed to be 0). Second, because the number of rejected ballots is very small relative to the number of ballots issued, using rejected ballots as the adjusted variable would have resulted in a much larger correction in percentage terms -- specifically, the correction would have required a 20\% change to the number of rejected ballots on average (with several exceeding 50\%), relative to a 0.6\% change to the number of ballots issued (with only one above 5\%, and none above 20\%).
